---
title: "Final Report for Intro to Data Science"
output: html_notebook
---

#Introduction#
   My project will answer my questions and confirm or deny my predictions. I predict that action and drama will be the most popular genres and it will be because of the actors depending on the point in time which in my test will be around the time of 2005-2010.
First lets Load some stuff from our library

#Prerequistest

```{r}
library(tidyverse)
library(ggplot2)
library(scales)
library(dplyr)
```
#Data
When we go to the movies we are influenced by the actors or genre. This will effect the outgoing total of income but what genre ends up being the end winner? The data set i will be using is as follows:

```{r}
Movies <- read_csv(file = "../data/IMDB_movies.csv")
Movies
```

#Record Data/Findings

  Firstly we want to determine what years to look at because alot of movies are produced each year menaing 10 years will be too much to look at, So I will narrow it down by making a graph showing by dots what years had the highest ratings in movies overall. Before all this when i looked at my data table, I was able to see movies recorded from the year of 2006 to 2016.
```{r}
  Movies2008 <- select(Movies, Year, Rating, Genre) %>%
  arrange(desc(Rating))
Movies2008
```
  From this narrowing down of data we can see that the year 2008 takes the cake with a clean 9.0 rating on the Movie "The Knight". We can see the most popular movies by making another table but for the movies rated in the year of 2008.
```{r}
Movies2008 %>%
  filter(Year == 2008)
  ggplot(data = Movies2008) +
  geom_point(aes(x = Genre, y = Rating ))
```
  The table shows that the highest rated movie is in the Genre category of: Action, Crime, and Drama. Now to see if there's a second runner up. I will determine the next highest rated movie in a different year.
```{r}
Toprate <- select(Movies,Year, Rating, Genre, Title) %>%
  arrange(desc(Rating))
Toprate
ggplot(data = Toprate) +
  geom_point(aes(x = Year, y = Rating))
```
  
  The second highest ranked movie (based on its tier in the table) is a movie called "Inception". This movie is rated with an 8.8 In the Genre category of: Action, Adventure, and Sci-Fi. The other movie below that was also rated an 8.8 was Dangal which is in the Genre category: Action, Biography, and Drama.
  
  1 Last thing I would like to investigate is what the lowest rated movie in 2008 is because on the graph it is very apparent. We can quickly re-use the command above and make it go from lowest Rating up to see what it is.
  
```{r}
Toprate <- select(Movies,Year, Rating, Genre, Title) %>%
  arrange(Rating)
Toprate
```
  Looking at this table now we can see why the dot was so low on the graph, This movie called "The Disaster" was rated a low 1.9 and its Genre category is only Comedy.

#Conclusion

  After all this further Investigation/Research on my data I can see That Action ad Drama based movies are the Most Popular types of movies (Based on 2008 1012, and 2014 ) and that in 2008 a movie hit all time low against all other movies in this dataset with a 1.9. :(
